Results

### 2024-04-19 Analysis/04_Summarise_results.Rmd
up vert.txt fix
Update 04_Summarise_results.Rmd

@@

## Loading empirical results
load("../Data/Processed/empirical_data-hist-present-native.rda")
empirical_hist <- bkp
load("../Data/Processed/empirical_data-prehist-present-native.rda")
empirical_prehist <- bkp

>>>>

TODO:
 - [ ] remove R2 on plots
 - [ ] finalise empirical plot
 - [ ] run simulations for 4D and 8D

@@

## Loading empirical results
load("../Data/Processed/empirical_data-hist-present-native.rda")
#empirical_data-hist-extant

empirical_hist <- bkp
load("../Data/Processed/empirical_data-prehist-present-native.rda")
#empirical_data-prehist-hist-prehist-extant
empirical_prehist <- bkp
